\documentclass{article}
\usepackage{sectsty}
\usepackage[utf8]{inputenc}
\usepackage{graphicx} % Required for inserting images

\title{Critical Analysis of Apple Inc.}
\author{Nishat Tasnim}
\date{December 2023}

\allsectionsfont{\underline}
\subsectionfont{\normalfont}

\begin{document}

\maketitle

\section{Apple Company}

Critical aspects of Apple's current state:

\begin{enumerate}
    \item Apple's market dominance fluctuates (1\%): Instead of simply stating a 1\% fluctuation, quantify the peaks and valleys to enhance the impact. For example, "Apple's market dominance oscillates between 20\% and 30\%, propelled by innovation during highs but dipping due to saturation during lows."
    
    \item Price tags bite into profits (\$2): Similar to point 1, provide specific price points or percentages to illustrate the challenge. For example, "Maintaining its premium image while remaining affordable is a balancing act. High-end iPhones priced above \$1,000 contribute significantly to revenue, but lower-priced models generate higher volume, posing a delicate profit margin dance."
    
    \item App Store ecosystem blooms (\#3): Replace "\#developer friction" with a more descriptive term like "developer discontent" or "app store policies debate" for clarity. You could also mention a specific example of friction, like revenue share disputes or app approval processes.
    
    \item Supply chain disruptions sting (4-): Expand on the types of disruptions and their specific impact. Mention specific global events or ethical concerns, like chip shortages, geopolitical tensions, or labor issues. Quantify the sting if possible, like "Supply chain disruptions, ranging from chip shortages to geopolitical tensions, sting with estimated production setbacks of 10\%."
    
    \item Creativity vs. stagnation: This point is well-stated but could be enriched by offering concrete examples of both fresh ideas and core strengths. Mention specific products or initiatives that exemplify innovation, and highlight aspects of Apple's identity that they should preserve.
\end{enumerate} By incorporating these suggestions, you can strengthen the clarity, detail, and impact of your writing, making it even more informative and insightful. Remember, these are just suggestions, and you can adapt them to best suit your specific goals and audience. Good luck! 

\section{Executive Summary}
Provide a concise overview of the key findings and recommendations regarding Apple Inc.'s current state.

\section{Introduction}

\subsection{Background}
Briefly introduce Apple Inc., its history, and its significant contributions to the technology industry.

\subsection{Objective}
State the purpose and goals of the critical analysis, outlining what aspects of Apple Inc.'s performance will be examined.

\section{Financial Performance}

\subsection{Revenue Trends}
Examine Apple's revenue trends over the past few years, identifying growth areas and potential challenges.

\subsection{Profitability Analysis}
Evaluate the factors affecting Apple's profitability, including product pricing and cost management.

\section{Market Positioning}

\subsection{Competitive Landscape}
Assess Apple's position in comparison to key competitors in the market.

\subsection{Customer Segmentation}
Explore the target audience and customer segments that Apple caters to.

\section{Innovation and Product Development}

\subsection{Product Portfolio}
Analyze Apple's product portfolio, highlighting successful products and areas for improvement.

\subsection{Research and Development}
Discuss Apple's investment in research and development and its impact on innovation.

\section{Corporate Social Responsibility}

\subsection{Environmental Initiatives}
Examine Apple's efforts toward sustainability and environmental responsibility.

\subsection{Social Impact}
Discuss Apple's involvement in social causes and community development.

\section{Conclusion}
Summarize the key findings from the analysis and provide recommendations for Apple's future strategies. \\\\ \textbf{\copyright 2023 Nishat Tasnim.}\\
\textbf{\textregistered All rights snuggled warmly in this cozy copyright nest.}


\end{document}