\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[utf8]{inputenc}
\usepackage{paralist}
\usepackage{enumitem}

\title{Programming Languages Overview}
\author{Nishat Tasnim}
\date{December 2023}

\begin{document}

\maketitle

\section{High-level Languages}

\begin{itemize}
    \item \textbf{Python}
          \begin{itemize}
              \item \textbf{Overview:}
                    \begin{itemize}
                        \item High-level, interpreted programming language.
                        \item Emphasizes readability and ease of use.
                        \item Widely adopted for various applications, e.g., \textit{web development} (Django, Flask), \textit{data science} (Pandas, NumPy), \textit{machine learning} (TensorFlow, PyTorch), and \textit{automation}.
                    \end{itemize}
              \item \textbf{Syntax:}
                    \begin{itemize}
                        \item Uses a clean and readable indentation-based syntax.
                        \item Facilitates a clear and expressive code structure.
                    \end{itemize}
              \item \textbf{Programming Paradigms:}
                    \begin{itemize}
                        \item Supports both procedural and object-oriented programming paradigms.
                        \item Allows functional programming concepts, enhancing code modularity and reusability.
                    \end{itemize}
              \item \textbf{Libraries and Frameworks:}
                    \begin{itemize}
                        \item Boasts a rich ecosystem with extensive standard libraries (\textit{e.g.,} datetime, os, math).
                        \item Prominent frameworks include \textit{Django} and \textit{Flask} for web development, \textit{TensorFlow} and \textit{PyTorch} for machine learning.
                    \end{itemize}
              \item \textbf{Community and Resources:}
                    \begin{itemize}
                        \item Features a large and active community of developers and enthusiasts.
                        \item Abundance of online resources, forums (\textit{e.g.,} Stack Overflow), and comprehensive documentation available for learners and professionals.
                    \end{itemize}
          \end{itemize}
          
    \item \textbf {Java}
    \begin{enumerate}[label=\roman*.]
        \item Platform-independent
        \item Object-oriented
        \item Strongly-typed
        \item Robust and secure
        \item Multi-threaded
    \end{enumerate}
    
    \item \textbf {JavaScript}
    \begin{enumerate}[label=\roman*.,start=6]
        \item Client-side scripting
        \item Asynchronous programming
        \item Event-driven, Lightweight and interpreted
        \item Widely used in web development
        \item Supports modern frameworks (e.g., React, Angular, Vue)
    \end{enumerate}
    
    \item C++
    \item C\#
    \item Ruby
    \item Swift
    \item Kotlin
    \item PHP
    \item TypeScript
\end{itemize}

\section{Web Development}

\begin{enumerate}
    \item \textbf{HTML/CSS (Markup and Style Sheet languages)}
    \begin{enumerate}
        \item \textbf{HTML (HyperText Markup Language):}
              \begin{enumerate}
                  \item Standard language for creating and designing web pages.
                  \item Uses a tag-based structure to define elements and content on a webpage.
                  \item Essential for structuring content such as headings, paragraphs, lists, links, images, and more.
              \end{enumerate}
        \item \textbf{CSS (Cascading Style Sheets):}
              \begin{itemize}
                  \item Style sheet language used for describing the presentation of a document written in HTML or XML.
                  \item Enables the separation of content and presentation, allowing for consistent styling across multiple pages.
                  \item Controls layout, colors, fonts, and other design aspects of a web page.
              \end{itemize}
    \end{enumerate}
    \item JavaScript
    \item TypeScript
    \item PHP
    \item Ruby
\end{enumerate}

\section{Systems Programming}

\begin{itemize}
    \item C++
    \item Rust
    \item Go (Golang)
    \item C
\end{itemize}

\section{Data Science and Statistics}

\begin{itemize}
    \item \textbf {Python}
    \begin{inparaenum}[(a)]
        \item NumPy
        \item Pandas
        \item Matplotlib
        \item Scikit-learn
        \item TensorFlow
        \item PyTorch
        \item Seaborn
        \item Statsmodels
    \end{inparaenum}
    \item R
    \item MATLAB
\end{itemize}

\section{Mobile App Development}

\begin{itemize}
    \item Swift
    \item Kotlin
    \item Java (Android)
    \item Objective-C (iOS)
\end{itemize}

\section{Scripting and Automation}

\begin{itemize}
    \item Shell Scripting (Bash/PowerShell)
    \item Python
    \begin{enumerate}[label=\alph*.]
        \item Versatile
        \item Automation
        \item Scripting
        \item Readability
    \end{enumerate}
    \item Perl
\end{itemize}

\section{Database Query Language}

\begin{itemize}
    \item SQL (Structured Query Language)
    \begin{enumerate}[label=\Alph*.]
        \item Data Retrieval
        \item Data Manipulation
        \item Data Definition
        \item Data Control
    \end{enumerate}
\end{itemize}

\section{Functional Programming}

\begin{itemize}
    \item Haskell
    \item Scala
\end{itemize}

\section{Other Languages}

\begin{itemize}
    \item Dart
    \item Lua
    \item Groovy
    \item Visual Basic
    \item Assembly Language
\end{itemize}

\end{document}